### 2020-01-27 frontmatter.tex
Paper 4 added.

The next focus of the thesis is the implementation of a minimal discrete-element lubrication/contact dynamics model for simulation of dense particle suspensions.
Here, the main ingredients include a frame-invariant, short-range lubrication model for spherical particles,
and a soft-core, stick/slide frictional contact model activated when particles overlap.
Furthermore, since contact interactions dominate at high particle concentrations,
we expect the methodology to be applicable for probing the jamming of non-spherical particles and the rheology of foams as well.

@@

Nästa fokus för avhandlingen är implementeringen av en minimal diskret-element smörjning/kontaktdynamik-modell för simulering av täta partikelsuspensioner.
Här innehåller huvudingredienserna en ram-invariant smörjningsmodell med kort räckvidd för sfäriska partiklar,
och en friktionskontaktmodell med mjukkärna, stick/slide aktiverad när partiklar överlappar varandra.
Eftersom kontaktinteraktioner dominerar vid höga partikelkoncentrationer,
vi förväntar oss att metodologin också är tillämplig för att undersöka fastklämning av icke-sfäriska partiklar och reologi för skum.

>>>>

The next focus of the thesis is the implementation of a minimal discrete-element lubrication/contact dynamics model for simulation of dense particle suspensions.
Two main ingredients of the model include
(i) a frame-invariant, short-range lubrication model for spherical particles, and
(ii) a soft-core, stick/slide frictional contact model activated when particles overlap.
Physically, since contact interactions dominate at high particle concentrations,
we expect the methodology to be applicable for probing the jamming of non-spherical particles and the rheology of foams as well.

@@

Nästa fokus för avhandlingen är implementeringen av en minimal diskretelementsmörjnings-/kontaktdynamikmodell för simulering av täta partikelsuspensioner.
Två huvudingredienser i modellen inkluderar
(i) en ram-invariant smörjmodell med kort räckvidd för sfäriska partiklar, och
(ii) en mjukkärna, stick/slide friktionskontaktmodell aktiverad när partiklar överlappar varandra.
Fysiskt eftersom kontaktinteraktioner dominerar vid höga partikelkoncentrationer,
vi förväntar oss att metodologin också är tillämplig för att undersöka fastklämning av icke-sfäriska partiklar och reologi för skum.
